Meta-analysis

### 2021-02-10 04_MetaAnalysis.Rmd
Remove code calculating estimate means instead of means dif

# adjust estimates to show absolute means
# results_mv <-
#    results_mv[2:6,] %>%
#    mutate(Effect = Effect + results_mv$Effect[1]) %>%
#    mutate(CI_lower = CI_lower + results_mv$CI_lower[1]) %>%
#    mutate(CI_upper = CI_upper + results_mv$CI_upper[1]) %>%
#    bind_rows(results_mv[1,]) %>%
#    mutate(index = c(2:6, 1)) %>%
#    arrange(index)

@@

```{r PM_Mv_Contrast}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
summary(glht(PM_mv_, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), test = adjusted("none"))
contrast_Ssum <-
   simple_summary(summary(glht(PM_mv_, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))
contrast_Ssum

>>>>

@@

```{r PM_Mv_Contrast}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
summary(glht(PM_mv, linfct = cbind(contrMat(rep(
   1, 6
), type = "Tukey"))), test = adjusted("none"))
contrast_Ssum <-
   simple_summary(summary(glht(PM_mv, linfct = cbind(
      contrMat(rep(1, 6), type = "Tukey")
   )), test = adjusted("none")))
contrast_Ssum
